---
title: "analyse_EP2019_trueresults"
author: "Stefan Hauﬂner"
date: "5 Juni 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(countrycode)
library(janitor)
library(lubridate)
library(openxlsx)
```

# Download all results from EP-Homepage

The german landing page is used here, but the code should work with other languages, too. You just need to change the url.

```{r}
url <- "https://europawahlergebnis.eu/tools/datenblatter-herunterladen/"

html <- read_html(url)

links <- html %>% 
  html_node(".download-datasheets--arrow-list") %>% 
  html_nodes("ul div") %>% .[3] %>% 
  html_nodes("ul li") %>% 
  html_nodes(".download-datasheets--link") %>% 
  html_attr("href") %>% 
  paste0("https://europawahlergebnis.eu",.)

cntry <- html %>% 
  html_node(".download-datasheets--arrow-list") %>% 
  html_nodes("ul div") %>% .[3] %>% 
  html_nodes("ul li") %>% 
  html_nodes(".download-datasheets--link") %>% 
  html_text() %>%
  tbl_df() %>% 
  mutate(id = rownames(.))

link_data <- tibble(cntry = cntry, links = links)
```

Make list of all results in all countries (or subnational entities). Basic data cleaning: Percentage points as numeric and update time as date-class and not as character values.

```{r}
results_ep19_national <- lapply(links, read.csv2) %>% 
  bind_rows(.id = "id") %>%
  left_join(., cntry, by = c("id" = "id")) %>% 
  tbl_df() %>% 
  mutate(VOTES_PERCENT = as.numeric(VOTES_PERCENT),
         UPDATE_TIME = ymd_hm(UPDATE_TIME))
```

So far the parties have just an ID like XX01, XX02... So we download the list for national party names and combine them with our data.

```{r}
list_party_names <- read_csv2("https://europawahlergebnis.eu/data-sheets/csv/2019-2024/election-results/parties.csv") %>% 
  mutate(DIVISION_ID = str_to_lower(DIVISION_ID))

results_ep19_national <- left_join(results_ep19_national, list_party_names, 
                                   by = c("value" = "DIVISION_ID","PARTY_ID" = "ID"))
```

Final data cleaning:
 + Selection of variables
 + save as CSV and XLSX

```{r}
results_ep19_national <- results_ep19_national %>% 
  select(DIVISION_ID = value, 
         PARTY_ID, 
         ACRONYM, 
         LABEL, 
         VOTES_PERCENT, 
         UPDATE_STATUS, 
         UPDATE_TIME)


write_csv2(results_ep19_national, "outputs/results_ep19_national.csv")
write.xlsx(results_ep19_national, "outputs/results_ep19_national.xlsx")
```



